Information Disclosure in Dynamic Innovation Contests

### 2025-05-31 paper/Paper.tex
update

%%%%%%%% Table, Figure and Diagram
%%%%%%%%%% Table
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
%%%%%%%%%% Figure
\usepackage{float}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{caption,}
\usepackage{subcaption}
%%%%%%%%%% Diagram Figure
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning}
\usepackage{varwidth}
%%%%%%%%%% Comments
\usepackage{comment}

@@

% Fill in data. If unknown, outcomment the field
\KEYWORDS{Digital Economy, Data Protection Regulation, Innovation Contest} 
%\HISTORY{......}

@@

@@

% Contest Deadline
Following \cite{ryvkin2022fight}, let's consider a dynamic contest with a fixed deadline. 
Suppose the contest is terminated when time $t=T>0$. 
Since the steady state estimation variance $\bar{S}$ is fixed as displayed above, the state of the game is fully characterized by a tuple $(\tilde{y}_t, t)$. 
At any time $0\le t<T$, player $i$ optimizes her effort level $q_{i,\tau}$ in the remaining contest period $\tau\in[t, T)$ according to the following optimization problem, 
\begin{equation}\label{v-def}
	V^i(\tilde{y}_{t}, t ; q_{j,t},\Theta_i) = \max_{\{q_{i,\tau}\}^T_{\tau=t}} 
	\mathbb{E}\left( \theta\cdot1_{\tilde{y}_T>0} - \int^T_tC_i(q_{i,\tau})d\tau \bigg|I_t\right) 
\end{equation}
where $\Theta_i \equiv\{\theta, \lambda, \sigma, c_i\}$, subject to constraints (\ref{filtered-x}), (\ref{filtered-S}) and $q_{i,\tau}\ge0$ for all $\tau\in[t,T)$.
The optimization problem for player $j$ is just symmetric to that of player $i$ as $V^j(\tilde{y}_t, t) = V^i(-\tilde{y}_t, t)$. 
The corresponding Hamilton-Jacobi-Bellman (HJB) equation for player $i$ is 
\begin{equation*}
0 = \max_{q_{i,t}\ge0}\left[-\frac{c_iq_i^2}{2} + V^i_{y}\cdot\left(q_{i,t}-q_{j,t}\right)+V^i_t + \frac{V^i_{yy}}{2}\lambda \bar{S}^2\right]
\end{equation*}
By definition, we have $\lambda \bar{S}^2 = \sigma^2$. 
Under the assumption of inner solution, we plug into the first order conditions $q_{i,t} = V^i_y/c_i$ and $q_{j,t} = -V^j_y/c_j$, we have the system of equations
\begin{equation*}
\begin{aligned}
\frac{1}{2c_i}(V^i_y)^2 + \frac{1}{c_j}V^i_yV^j_y + V^i_t + V^i_{yy}\frac{\sigma^2}{2} = 0\\
\frac{1}{2c_j}(V^j_y)^2 + \frac{1}{c_i}V^j_yV^i_y + V^j_t + V^j_{yy}\frac{\sigma^2}{2} = 0
\end{aligned}
\end{equation*}
subject to boundary conditions $V^i(-\infty, t) = 0$, $V^i(+\infty, t) = \theta$, $V^j(-\infty, t) = \theta$, $V^j(+\infty, t)=0$, $V^i(\tilde{y}_T, T) = \theta \cdot 1_{\tilde{y}_T > 0}$ and $V^j(\tilde{y}_T, T) = \theta \cdot 1_{\tilde{y}_T < 0}$.

@@

\begin{lemma}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $m_{i(j)}(\tilde{y}_t, t) :\mathbb{R}\times[0, T)\to\mathbb{R}_+$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(\tilde{y}_t, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = \tilde{y}_t / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
\end{lemma}

The variables $w_{i(j)}$ represent the abilities of two players, while $\rho_{i(j)}$ normalizes $w_{i(j)}$ into the interval $(-1, 1)$. 
It is not hard to see that $\gamma(\cdot)$ is strictly increasing on $(-1,1)$, ranging from $-\infty$ to $+\infty$. 
Moreover, the equilibrium effort $m_{i(j)}$ can be represented to the product of $\phi(y; 0, \sigma^2(T-t))$, the probability density of normal distribution with mean zero and variance $\sigma^2(T-t)$ at the state $y$ and an amplitude factor that only depends on the composite variable $z$.

@@

@@

%% Data: Contest setting
The first component consists of essential contest details, including the contest duration, prize structure, information disclosure policy, and other governing rules.
%%%% Prob 1
Contrary to the assumptions of our model, a typical contest usually involves multiple teams rather than just two.
In Section~\ref{sec-kaggle-application}, we focus on the two strongest participants in each contest for analysis; further discussion on this choice is provided in Section~\ref{sect-extension}.
%%%% Prob 2
Furthermore, many contests adopt complex prize structures, offering multiple awards rather than following a winner-takes-all format.
In Section~\ref{sec-kaggle-application}, we begin by selecting contests that offer a single prize awarded in USD.
Extensions to more general prize structures are presented in Section~\ref{sect-extension}.

@@

\section{Empirical Application}\label{sec-kaggle-application}

@@

If $S$ is in steady state $dS/dt = 0$ $\Leftrightarrow$ $S = \bar{S} \equiv \sigma/\sqrt{\lambda}$. 
If $S$ is not in steady state, i.e. $S\not=\bar{S}$, we first isolate the two variables and get 
\begin{equation*}
	\frac{dS}{\sigma-\lambda S^2} = dt
\end{equation*}
Then, we take the integral on both sides
\begin{equation*}
    t = \int \frac{dS}{\sigma-\lambda S^2} = \frac{1}{\sigma\sqrt{\lambda}} \int \frac{dS\sqrt{\lambda}/\sigma}{1 - (S\sqrt{\lambda}/\sigma)^2} \equiv \frac{1}{\sigma\sqrt{\lambda}}\int \frac{du}{1-u^2} 
\end{equation*}
where $u = S\sqrt{\lambda}/\sigma = S/\bar{S}$. Hence, 
\begin{equation*}
    \sigma\sqrt{\lambda}\cdot t = \begin{cases}
        \tanh^{-1}(u)-K_1, & \text{if } |u|<1\\
        \coth^{-1}(u)-K_2, & \text{if } |u|>1
    \end{cases} = \begin{cases}
        \tanh^{-1}(S/\bar{S})-K_1, & \text{if } S<\bar{S}\\
        \coth^{-1}(S/\bar{S})-K_2, & \text{if } S>\bar{S} 
\end{cases}
\end{equation*}
Thus, we conclude the non-steady state case that 
\begin{equation*}
	S = \begin{cases}
		\bar{S}\cdot\tanh(\sigma\sqrt{\lambda}\cdot t + K_1), & \text{if } S<\bar{S}\\
		\bar{S}\cdot\coth(\sigma\sqrt{\lambda}\cdot t + K_2), & \text{if } S>\bar{S} 
	\end{cases}
\end{equation*}
Finally, we determine the constants $K_1$, $K_2$ by the initial condition $S_0$ and have 
\begin{align*}
	K_1 &= \tanh^{-1}(S_0/\bar{S})\\
	K_2 &= \coth^{-1}(S_0/\bar{S})
\end{align*}

@@

>>>>

%%%%%%%% Table, Figure and Diagram
%%%%%%%%%% Table
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{booktabs}
%%%%%%%%%% Figure
\usepackage{float}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{caption,}
\usepackage{subcaption}
%%%%%%%%%% Diagram Figure
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning}
\usepackage{varwidth}
%%%%%%%%%% Comments
\usepackage{comment}

@@

% Fill in data. If unknown, outcomment the field
\KEYWORDS{Bayesian Statistics, Structural Estimation, Crowdsourcing Contest, Dynamic Contest} 
%\HISTORY{......}

@@

Structural Estimation - \cite{jiang2022role}.

@@

% Contest Deadline
Following \cite{ryvkin2022fight}, let's consider a dynamic contest with a fixed deadline. 
Suppose the contest is terminated when time $t=T>0$. 
Since the steady state estimation variance $\bar{S}$ is fixed as displayed above, the state of the game is fully characterized by a tuple $(\tilde{y}_t, t)$. 
At any time $0\le t<T$, player $i$ optimizes her effort level $q_{i,\tau}$ in the remaining contest period $\tau\in[t, T)$ according to the following optimization problem, 
\begin{equation}\label{v-def}
	V^i(\tilde{y}_{t}, t ; q_{j,t},\Theta_i) = \max_{\{q_{i,\tau}\}^T_{\tau=t}} 
	\mathbb{E}\left( \theta\cdot1_{\tilde{y}_T>0} - \int^T_tC_i(q_{i,\tau})d\tau \bigg|I_t\right) 
\end{equation}
where $\Theta_i \equiv\{\theta, \lambda, \sigma, c_i\}$, subject to constraints (\ref{filtered-x}), (\ref{filtered-S}) and $q_{i,\tau}\ge0$ for all $\tau\in[t,T)$.
The optimization problem for player $j$ is just symmetric to that of player $i$ as $V^j(\tilde{y}_t, t) = V^i(-\tilde{y}_t, t)$. 
The corresponding Hamilton-Jacobi-Bellman (HJB) equation for player $i$ is 
\begin{equation*}
0 = \max_{q_{i,t}\ge0}\left[-\frac{c_iq_i^2}{2} + V^i_{y}\cdot\left(q_{i,t}-q_{j,t}\right)+V^i_t + \frac{V^i_{yy}}{2}\lambda \bar{S}^2\right].
\end{equation*}
By definition, we have $\lambda \bar{S}^2 = \sigma^2$. 
Under the assumption of inner solution, we plug into the first order conditions $q_{i,t} = V^i_y/c_i$ and $q_{j,t} = -V^j_y/c_j$, we have the system of equations
\begin{equation*}
\begin{aligned}
\frac{1}{2c_i}(V^i_y)^2 + \frac{1}{c_j}V^i_yV^j_y + V^i_t + V^i_{yy}\frac{\sigma^2}{2} = 0\\
\frac{1}{2c_j}(V^j_y)^2 + \frac{1}{c_i}V^j_yV^i_y + V^j_t + V^j_{yy}\frac{\sigma^2}{2} = 0
\end{aligned}
\end{equation*}
subject to boundary conditions $V^i(-\infty, t) = 0$, $V^i(+\infty, t) = \theta$, $V^j(-\infty, t) = \theta$, $V^j(+\infty, t)=0$, $V^i(\tilde{y}_T, T) = \theta \cdot 1_{\tilde{y}_T > 0}$ and $V^j(\tilde{y}_T, T) = \theta \cdot 1_{\tilde{y}_T < 0}$.

@@

\begin{theorem}[\citealt{ryvkin2022fight}]
In the Markov perfect equilibrium, the players’ efforts in state $m_{i(j)}(\tilde{y}_t, t) :\mathbb{R}\times[0, T)\to\mathbb{R}_+$ are given by
\begin{equation}\label{eq-equilibrium-effort}
m_{i(j)}(\tilde{y}_t, t) = \frac{e^{-z^2/2}}{\sqrt{2\pi\sigma^2(T-t)}}\cdot \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]
\end{equation}
where $z = \tilde{y}_t / (\sigma\sqrt{T-t})$, $\rho(z) = \gamma^{-1}\left(\Phi(z)\left[\gamma(\rho_{i})+\gamma(\rho_{j})\right]-\gamma(\rho_{j})\right)$ and 
\begin{equation*}
\gamma(u) = \frac{u}{1-u^2} + \frac{1}{2}\ln\frac{1+u}{1-u},\quad u\in(-1,1)
\end{equation*}
\begin{equation*}
\rho_{i} = \frac{e^{w_{i}}+e^{-w_{j}}-2}{e^{w_{i}}-e^{-w_{j}}},
\quad
\rho_{j} = \frac{e^{w_{j}}+e^{-w_{i}}-2}{e^{w_{j}}-e^{-w_{i}}},
\quad
w_{i(j)} = \frac{\theta}{\sigma^2 c_{i(j)}}.
\end{equation*}
Moreover, the total expected effort at time $t$, defined by $M(\tilde{y}_t, t) := \mathbb{E}\left[\int^T_t m_i(\tilde{y}_s, s) + m_j(\tilde{y}_s, s)ds\right]$, is given by $M(\tilde{y}_t, t) = \sigma \sqrt{T-t} q(z)$, where $q(z)$ is determined by the ordanary differential equation 
\begin{equation}
\begin{aligned}
&q''(z) + \left[4A_+(z)e^{-z^2/2}+z\right]q'(z) - q(z) + 4A_-(z)e^{-z^2/2} = 0\\
&A_-(z) = \frac{\gamma(\rho_1) + \gamma(\rho_2)}{2\sqrt{2\pi}}[1 - \rho(z)^2],
\quad A_+(z) = A_-(z)\rho(z)
\end{aligned}
\end{equation}
subject to the boundary conditions $q(z)\to0$ as $z\to\pm\infty$. 
Specifically, when $c_i = c_j$, we have 
\begin{equation}
M(\tilde{y}_t, t) = \frac{2w\sigma\sqrt{T-t}}{\sqrt{2\pi}}e^{-z^2/2} + o(w)
\end{equation}
\end{theorem}

The variables $w_{i(j)}$ measure the abilities of two players, while $\rho_{i(j)}$ normalizes $w_{i(j)}$ into the interval $(0, 1)$. 
Specifically, $\rho_{i(k)}$ and $w_{i(j)}$ are in a strictly increasing bijective relationship. 
It is not hard to see that function $\gamma(\cdot)$ is strictly increasing on $(-1,1)$, ranging from $-\infty$ to $+\infty$. 
The function $\rho(\cdot)$ is strictly increasing on $\mathbb{R}$, ranging from $-1$ to $1$. 
%% Forms
The equilibrium effort $m_{i(j)}$ can be represented to the product of two components:
the normal density function $\phi(y; 0, \sigma^2(T-t))$, which represents the probability density of a normal distribution with mean zero and variance $\sigma^2(T-t)$ evaluated at state $y$, and an amplitude factor $K_{i(j)}(z; \theta, \sigma, c_i, c_j) := \frac{\sigma^2}{2}\left[\gamma(\rho_{i}) + \gamma(\rho_{j})\right]\left[1-\rho(z)^2\right]\left[1 \pm \rho(z)\right]$. 
The normal density governs the concentration of competitive intensity over state, i.e., perceived output gap $\tilde{y}_t$, while the amplitude term $K_{i(j)}$ modulates the asymmetry (or skewness) of effort allocation between players.

It is also evident that the parameters $\theta$, $c_i$ and $c_j$ influence equilibrium effort exclusively through the amplitude component.
In contrast, the effect of $\sigma$ is more nuanced, as it enters both the normal density and amplitude terms. 
By the form of (\ref{eq-equilibrium-effort}), we can do some comparative analysis:

\subsection{Implications on the Contest Design}

@@

\newpage

@@

%% Data: Contest setting
The first component consists of essential contest details, including the contest duration, prize structure, information disclosure policy, and other governing rules.
%%%% Prob 1
Contrary to the assumptions of our model, a typical contest usually involves multiple teams rather than just two.
In Section~\ref{sec-kaggle-application}, we focus on the two strongest participants in each contest for analysis.
%%%% Prob 2
Furthermore, many contests adopt complex prize structures, offering multiple awards rather than following a winner-takes-all format.
In Section~\ref{sec-kaggle-application}, we begin by selecting contests that offer a single prize awarded in USD.

@@

\section{Empirical Application}
\label{sec-kaggle-application}

@@

If $S$ is in steady state $dS/dt = 0$ $\Leftrightarrow$ $S = \bar{S} \equiv \sigma/\sqrt{\lambda}$. 
If $S$ is not in steady state, i.e. $S\not=\bar{S}$, we first isolate the two variables and get 
\begin{equation*}
	\frac{dS}{\sigma-\lambda S^2} = dt
\end{equation*}
Then, we take the integral on both sides
\begin{equation*}
    t = \int \frac{dS}{\sigma-\lambda S^2} = \frac{1}{\sigma\sqrt{\lambda}} \int \frac{dS\sqrt{\lambda}/\sigma}{1 - (S\sqrt{\lambda}/\sigma)^2} \equiv \frac{1}{\sigma\sqrt{\lambda}}\int \frac{du}{1-u^2} 
\end{equation*}
where $u = S\sqrt{\lambda}/\sigma = S/\bar{S}$. Hence, 
\begin{equation*}
    \sigma\sqrt{\lambda}\cdot t = \begin{cases}
        \tanh^{-1}(u)-K_1, & \text{if } |u|<1\\
        \coth^{-1}(u)-K_2, & \text{if } |u|>1
    \end{cases} = \begin{cases}
        \tanh^{-1}(S/\bar{S})-K_1, & \text{if } S<\bar{S}\\
        \coth^{-1}(S/\bar{S})-K_2, & \text{if } S>\bar{S} 
\end{cases}
\end{equation*}
Thus, we conclude the non-steady state case that 
\begin{equation*}
	S = \begin{cases}
		\bar{S}\cdot\tanh(\sigma\sqrt{\lambda}\cdot t + K_1), & \text{if } S<\bar{S}\\
		\bar{S}\cdot\coth(\sigma\sqrt{\lambda}\cdot t + K_2), & \text{if } S>\bar{S} 
	\end{cases}
\end{equation*}
Finally, we determine the constants $K_1$, $K_2$ by the initial condition $S_0$ and have 
\begin{align*}
	K_1 = \tanh^{-1}(S_0/\bar{S}),\quad
	K_2 = \coth^{-1}(S_0/\bar{S})
\end{align*}

@@

\begin{longtable}{cccccccccccrc}
\toprule
\multirow{2}{*}{\makecell{\rule{0pt}{2.5ex}Contest\\Id}} & 
\multirow{2}{*}{\makecell{\rule{0pt}{2.5ex}$N^i$}} & 
\multirow{2}{*}{\makecell{\rule{0pt}{2.5ex}$N^j$}} & 
\multirow{2}{*}{\makecell{\rule{0pt}{2.5ex}Prize\\(k, USD)}} & 
\multirow{2}{*}{\makecell{\rule{0pt}{2.5ex}Public\\Data \%}} & 
\multicolumn{6}{c}{Bayesian Posterior Mean} &
\multicolumn{2}{c}{Cross Validation} \\
\cmidrule(lr){6-11}
\cmidrule(lr){12-13}
 &  &  &  &  & $\lambda$ & $\sigma$ & $\mu_0$ & $c_i$ & $c_j$ & $r$ & \makecell{$\lambda^\text{MLE}$} & $\sigma^\text{MLE}$ \\
\midrule
2445 & 7 & 19 & 5.00 & 25 & 15.377 & 0.980 & -0.089 & 4.304 & 3.154 & 2.088 & 1539.379 & 0.394 \\
2454 & 19 & 13 & 0.15 & 62 & 15.016 & 1.030 & 4.377 & 0.688 & 0.810 & 18.035 & 932.836 & 0.659 \\
2464 & 11 & 12 & 0.95 & 20 & 9.844 & 2.325 & -0.474 & 1.631 & 1.380 & 14.217 & 99.556 & 3.741 \\
2478 & 13 & 11 & 0.95 & 30 & 13.636 & 0.673 & -0.444 & 3.171 & 3.811 & 6.333 & 19406.675 & 0.770 \\
2489 & 12 & 21 & 0.50 & 10 & 16.650 & 0.576 & 0.431 & 3.535 & 2.303 & 11.210 & 5759.075 & 0.843 \\
2549 & 13 & 15 & 0.50 & 30 & 12.214 & 1.357 & -1.055 & 1.409 & 1.157 & 14.758 & 525.201 & 2.891 \\
2551 & 48 & 30 & 1.50 & 30 & 26.143 & 0.539 & -0.286 & 3.207 & 4.141 & 6.669 & 140015.172 & 0.512 \\
2667 & 55 & 67 & 30.00 & 50 & 16.977 & 1.695 & 0.758 & 3.919 & 3.803 & 1.184 & 1.805 & 5.430 \\
2749 & 22 & 22 & 3.00 & 42 & 20.708 & 0.701 & 0.906 & 4.308 & 4.022 & 4.367 & 37219.066 & 0.340 \\
2762 & 12 & 21 & 1.00 & 35 & 11.659 & 0.779 & 1.068 & 3.103 & 2.237 & 13.005 & 20.923 & 1.244 \\
2860 & 9 & 6 & 1.00 & 30 & 12.735 & 0.816 & 0.133 & 3.096 & 3.728 & 6.933 & 33538.355 & 0.034 \\
3064 & 13 & 5 & 0.20 & 25 & 14.106 & 0.630 & -0.788 & 1.160 & 2.780 & 13.821 & 8206710.757 & 0.263 \\
3080 & 25 & 27 & 0.09 & 25 & 23.442 & 0.531 & -1.217 & 0.623 & 0.643 & 19.327 & 150384.896 & 0.187 \\
3288 & 20 & 10 & 1.00 & 0 & 10.864 & 3.729 & -1.169 & 0.822 & 1.750 & 15.448 & 2.179 & 0.616 \\
3338 & 31 & 29 & 1.50 & 30 & 24.827 & 0.541 & 0.203 & 3.508 & 3.345 & 7.687 & 8200.515 & 0.244 \\
3353 & 26 & 17 & 10.00 & 30 & 16.307 & 1.232 & -0.249 & 3.749 & 4.305 & 2.066 & 22001.196 & 1.410 \\
3366 & 16 & 11 & 0.50 & 50 & 15.653 & 0.693 & -1.936 & 2.055 & 3.018 & 13.340 & 4849.451 & 0.499 \\
3507 & 9 & 13 & 0.50 & 33 & 14.030 & 1.055 & 0.529 & 2.440 & 1.891 & 14.095 & 163.652 & 1.101 \\
3509 & 8 & 13 & 0.20 & 30 & 12.714 & 0.741 & -0.024 & 2.491 & 1.513 & 13.807 & 3167.382 & 0.884 \\
3526 & 15 & 13 & 5.00 & 20 & 15.809 & 0.793 & -0.053 & 4.127 & 4.159 & 1.280 & 11651.555 & 0.242 \\
3641 & 7 & 41 & 1.50 & 43 & 20.406 & 0.579 & 0.615 & 4.292 & 1.875 & 3.434 & 2447.287 & 0.319 \\
3774 & 29 & 26 & 0.50 & 50 & 23.554 & 0.537 & -0.997 & 2.580 & 2.898 & 13.300 & 29.891 & 0.952 \\
3800 & 21 & 28 & 3.00 & 15 & 20.046 & 0.820 & 3.384 & 4.322 & 3.599 & 6.632 & 1174.496 & 0.625 \\
3926 & 25 & 20 & 0.30 & 25 & 22.016 & 0.547 & -0.047 & 1.237 & 1.529 & 13.393 & 4798.921 & 0.332 \\
3928 & 15 & 21 & 0.68 & 70 & 19.525 & 0.584 & -0.421 & 3.604 & 3.051 & 11.838 & 87393.056 & 0.139 \\
3929 & 35 & 31 & 8.00 & 50 & 5.865 & 3.653 & 0.062 & 3.165 & 3.520 & 10.320 & 4794.303 & 5.862 \\
3960 & 47 & 50 & 8.00 & 40 & 28.973 & 0.883 & -0.992 & 4.624 & 4.670 & 3.583 & 624.827 & 0.514 \\
4031 & 6 & 61 & 5.00 & 30 & 19.132 & 0.831 & 0.605 & 4.487 & 1.975 & 3.021 & 125709.402 & 1.214 \\
4104 & 8 & 6 & 20.00 & 20 & 10.864 & 2.116 & 0.036 & 3.729 & 3.994 & 0.742 & 42409.966 & 0.141 \\
4366 & 31 & 31 & 8.00 & 2 & 23.414 & 0.913 & -0.434 & 4.367 & 4.554 & 2.979 & 3601.181 & 0.487 \\
4407 & 44 & 51 & 4.00 & 19 & 14.573 & 1.670 & 0.070 & 3.591 & 3.238 & 12.165 & 56.026 & 2.693 \\
4453 & 15 & 18 & 2.00 & 30 & 17.165 & 0.617 & 1.204 & 4.110 & 3.071 & 2.607 & 47662.222 & 0.892 \\
4477 & 7 & 11 & 2.00 & 50 & 11.870 & 1.104 & -3.305 & 3.867 & 3.222 & 5.142 & 2524.322 & 0.325 \\
4488 & 11 & 8 & 2.00 & 1 & 8.033 & 5.347 & 1.108 & 2.160 & 2.843 & 12.739 & 1903.540 & 1.559 \\
4493 & 19 & 14 & 10.00 & 40 & 16.683 & 1.161 & -0.191 & 3.883 & 4.306 & 1.567 & 7787.118 & 0.355 \\
4657 & 66 & 62 & 4.00 & 30 & 34.581 & 0.559 & 0.330 & 4.657 & 4.691 & 3.410 & 1221277.563 & 0.205 \\
4699 & 13 & 22 & 5.00 & 30 & 18.734 & 0.765 & 0.112 & 4.242 & 3.833 & 1.207 & 223019.351 & 0.211 \\
4986 & 16 & 5 & 10.00 & 50 & 13.378 & 1.203 & -0.029 & 3.287 & 4.306 & 1.214 & 80756.892 & 0.393 \\
5056 & 18 & 35 & 5.00 & 33 & 21.957 & 0.720 & -0.780 & 4.484 & 4.094 & 2.763 & 536274.232 & 0.324 \\
5144 & 11 & 9 & 20.00 & 20 & 7.244 & 3.118 & 10.283 & 3.617 & 3.737 & 1.411 & 3752.980 & 2.695 \\
5174 & 42 & 47 & 3.00 & 50 & 23.823 & 0.744 & -1.240 & 4.346 & 4.162 & 8.369 & 292993.349 & 1.622 \\
5229 & 28 & 31 & 15.00 & 10 & 12.332 & 3.417 & 0.320 & 3.961 & 3.564 & 6.028 & 14.707 & 2.880 \\
5261 & 45 & 43 & 10.00 & 30 & 26.183 & 0.965 & -1.578 & 4.361 & 4.651 & 2.525 & 83664.604 & 0.965 \\
5357 & 36 & 22 & 5.00 & 30 & 22.768 & 0.774 & 1.093 & 4.028 & 4.506 & 3.022 & 8980.088 & 0.354 \\
5390 & 22 & 17 & 4.00 & 30 & 17.724 & 0.819 & 0.513 & 3.650 & 4.317 & 4.262 & 1165.060 & 1.086 \\
5497 & 44 & 24 & 4.00 & 30 & 25.292 & 0.652 & 0.642 & 4.231 & 4.571 & 3.005 & 9784887.950 & 0.233 \\
6322 & 23 & 26 & 10.00 & 66 & 9.106 & 2.653 & -0.405 & 3.753 & 3.536 & 5.852 & 48.308 & 3.981 \\
6927 & 19 & 16 & 4.00 & 1 & 18.477 & 0.918 & -0.601 & 3.925 & 4.247 & 4.178 & 8317.660 & 0.272 \\
7115 & 19 & 39 & 4.00 & 30 & 15.827 & 0.848 & 0.444 & 4.314 & 3.226 & 3.401 & 408806.642 & 1.469 \\
7162 & 51 & 14 & 1.00 & 50 & 20.424 & 0.808 & -1.269 & 1.209 & 4.010 & 8.932 & 39471.599 & 1.093 \\
7634 & 52 & 44 & 2.00 & 2 & 23.259 & 0.568 & 0.761 & 3.767 & 4.307 & 8.242 & 7635.257 & 1.509 \\
7878 & 5 & 7 & 4.00 & 29 & 9.554 & 1.484 & -0.612 & 3.815 & 3.285 & 1.450 & 619.191 & 0.875 \\
8076 & 34 & 29 & 6.00 & 10 & 22.880 & 0.806 & -1.387 & 4.321 & 4.419 & 2.903 & 8518.348 & 1.134 \\
8078 & 29 & 32 & 4.00 & 36 & 8.066 & 1.796 & 1.664 & 3.587 & 3.088 & 10.469 & 143.391 & 5.352 \\
8219 & 16 & 23 & 0.40 & 22 & 15.559 & 0.604 & -0.087 & 2.601 & 1.940 & 14.337 & 674373.206 & 1.542 \\
8396 & 53 & 59 & 0.50 & 1 & 13.606 & 1.385 & 7.016 & 0.880 & 0.767 & 16.517 & 1158.201 & 2.451 \\
8540 & 30 & 38 & 5.00 & 18 & 22.939 & 0.840 & -0.117 & 4.326 & 4.212 & 4.251 & 7531.700 & 1.251 \\
9120 & 52 & 44 & 10.00 & 20 & 28.586 & 0.876 & -0.006 & 4.690 & 4.746 & 1.789 & 49444.336 & 0.219 \\
9949 & 21 & 35 & 5.00 & 20 & 21.022 & 0.923 & 1.016 & 4.539 & 3.565 & 3.200 & 14679.381 & 0.563 \\
10200 & 22 & 25 & 4.00 & 9 & 15.905 & 1.513 & -7.127 & 3.619 & 3.583 & 6.466 & 28779.845 & 1.034 \\
10684 & 16 & 58 & 4.00 & 57 & 18.929 & 0.659 & -7.058 & 4.450 & 3.642 & 4.785 & 32.622 & 1.342 \\
13333 & 18 & 19 & 2.00 & 25 & 19.948 & 0.638 & 0.168 & 3.975 & 3.913 & 6.246 & 85026.315 & 0.079 \\
14242 & 68 & 37 & 3.00 & 20 & 31.135 & 0.558 & 0.383 & 4.266 & 4.663 & 5.096 & 2915.546 & 0.372 \\
14420 & 56 & 20 & 20.00 & 22 & 13.393 & 1.571 & -3.492 & 3.144 & 4.609 & 1.464 & 5.884 & 5.899 \\
18045 & 40 & 50 & 4.00 & 30 & 26.932 & 0.654 & -3.178 & 4.269 & 4.344 & 3.532 & 187.042 & 0.809 \\
19018 & 63 & 67 & 8.00 & 30 & 29.425 & 0.835 & 1.891 & 4.634 & 4.360 & 2.918 & 18544.514 & 0.863 \\
19991 & 22 & 50 & 4.00 & 20 & 24.460 & 0.658 & 0.062 & 4.599 & 3.990 & 3.472 & 925.409 & 1.058 \\
20270 & 20 & 16 & 4.00 & 30 & 18.848 & 0.815 & -0.255 & 3.707 & 4.250 & 3.938 & 293.230 & 0.531 \\
21669 & 38 & 37 & 1.00 & 21 & 17.621 & 0.831 & -1.649 & 1.917 & 2.520 & 14.959 & 2382.409 & 2.604 \\
22962 & 23 & 18 & 4.00 & 24 & 17.168 & 0.879 & -1.295 & 3.760 & 4.158 & 4.583 & 7906.999 & 1.143 \\
23249 & 21 & 40 & 1.00 & 16 & 24.123 & 0.532 & 0.538 & 2.978 & 2.075 & 7.226 & 1795533.078 & 0.101 \\
23652 & 24 & 24 & 1.00 & 20 & 20.607 & 0.643 & -0.193 & 2.862 & 3.456 & 14.124 & 87142.434 & 1.056 \\
37077 & 11 & 46 & 4.00 & 24 & 19.329 & 0.886 & 0.584 & 4.311 & 2.254 & 3.507 & 10417.255 & 1.563 \\
38128 & 27 & 52 & 8.00 & 42 & 25.657 & 0.808 & -0.562 & 4.687 & 4.444 & 1.655 & 23943.751 & 0.263 \\
38760 & 10 & 17 & 5.00 & 33 & 12.412 & 1.155 & 0.026 & 4.192 & 3.255 & 2.936 & 6387644.371 & 2.551 \\
\bottomrule
\end{longtable}
